Patient movements

### 2024-01-24 analysis/patient-tracking.Rmd
minor fixes and qctr analysis draft for scientific meeting presentation

```{r}
df <- readRDS("../data-clean/patient-tracking/augmented-and-combined-data.rds")
```

@@

@@

```{r}
time_in_clin <- df %>%
  group_by(date, patient_id) %>%
  summarize(tracking_end = first(tracking_end),
            `Clinic` = n(),
            `Waiting room` = sum(is_waitingroom),
            `TB room` = sum(is_tbroom),
            `Corridor` = sum(is_passage)) %>%
  ungroup() %>%
  mutate(across(c(`Clinic`, `Waiting room`, `TB room`, `Corridor`), ~ .x / 60))

@@

```{r}
# number of close contacts <1m for >1min
no_close_contacts <- df %>%
  unnest(cols = closeContacts) %>%
  group_by(date, patient_id, closeContacts, tracking_end) %>%
  summarise(n_time = n(),
            tracking_end = first(tracking_end)) %>%
  ungroup() %>%
  group_by(date, patient_id) %>%
  summarize(n_cc = sum(n_time > 60),
            tracking_end = first(tracking_end)) %>%
  ungroup()

time_close_contacts <- df %>%
  mutate(has_closeContact = ifelse(sapply(closeContacts, length) >= 1, T, F)) %>%
  group_by(date, patient_id) %>%
  summarize(cc_time = sum(has_closeContact) / 60,
            tracking_end = first(tracking_end)) %>%
  ungroup()

@@

time_pl <- clinic_occupancy %>%
  ggplot(aes(x = time, y = value, color = date)) +
  geom_step() +
  facet_wrap(~ variable) +
  coord_cartesian(expand = F) +
  scale_x_datetime(date_breaks = "3 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(y = "Number of people", title = "Occupancy over time", subtitle = "Number of active tracks per room over time") +
  theme_custom(14) +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = "bottom"
        )

@@

```{r}
spatial_pl <- plot_spatial(
  ggplot(data = df, mapping = aes(x = x, y = y)) +
    geom_bin2d(binwidth = 200),
  text_descr = 14) +
  labs(fill = "Number of tracks", title = "Spatial occupancy", subtitle = "Total number of tracks per grid cell") +
  scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log10", 
                    breaks = c(1, 10, 100, 1000, 10000)) +
  theme(legend.position = c(0.825,0.075), legend.direction = "horizontal") +
  guides(fill = guide_legend(nrow = 2, title.position = "top"))

>>>>

```{r}
df <- readRDS("../data-clean/patient-tracking/augmented-and-combined-data.rds")

# filter considered clinical attendees
df_matched <- do.call(rbind, lapply(unique(df$date), function(d) readRDS(paste0("../data-clean/patient-tracking/matched-clinical/", d, ".rds")))) %>%
  mutate(date = as.Date(time))
df_filt <- filter(df, paste(date, patient_id) %in% unique(paste(df_matched$date, df_matched$patient_id)))
```

@@

```{r}
n_distinct(paste(df$date, df$patient_id))
n_distinct(paste(df_filt$date, df_filt$patient_id))
```

@@

```{r}
time_in_clin <- df_filt %>%
  group_by(date, patient_id) %>%
  summarize(tracking_end = first(tracking_end),
            `Clinic` = n(),
            `Waiting room` = sum(is_waitingroom),
            `TB room` = sum(is_tbroom),
            `Corridor` = sum(is_passage)) %>%
  ungroup() %>%
  mutate(across(c(`Clinic`, `Waiting room`, `TB room`, `Corridor`), ~ .x / 60))

@@

```{r}
# number of close contacts <1m for >1min
no_close_contacts <- df_filt %>%
  unnest(cols = closeContacts) %>%
  group_by(date, patient_id, closeContacts, tracking_end) %>%
  summarise(n_time = n(),
            tracking_end = first(tracking_end)) %>%
  ungroup() %>%
  group_by(date, patient_id) %>%
  summarize(n_cc = sum(n_time > 60),
            tracking_end = first(tracking_end)) %>%
  ungroup()

time_close_contacts <- df_filt %>%
  mutate(has_closeContact = ifelse(sapply(closeContacts, length) >= 1, T, F)) %>%
  group_by(date, patient_id) %>%
  summarize(cc_time = sum(has_closeContact) / 60,
            tracking_end = first(tracking_end)) %>%
  ungroup()

@@

time_pl <- clinic_occupancy %>%
  ggplot(aes(x = time, y = value, color = date)) +
  geom_step() +
  ggh4x::facet_wrap2(~ variable, axes = "x", remove_labels = "all") +
  coord_cartesian(expand = F) +
  scale_x_datetime(date_breaks = "3 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(y = "Number of people", title = "Occupancy over time", subtitle = "Number of active tracks per room over time") +
  theme_custom(14) +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = "bottom")

@@

```{r}
spatial_pl <- plot_spatial(
  ggplot(data = df, mapping = aes(x = x, y = y)) +
    geom_bin2d(binwidth = 200),
  text_descr = 14) +
  labs(fill = "Number of tracks", title = "Spatial occupancy", subtitle = "Total number of tracks per grid cell") +
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log10", labels = scales::comma) +
  # scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log10", 
  #                   breaks = c(1, 10, 100, 1000, 10000)) +
  theme(legend.position = c(0.82,0.095), legend.direction = "horizontal",
        legend.key.height = unit(0.2, "cm"), legend.key.width = unit(.8, "cm")) +
  guides(fill = guide_colorbar(title.position = "top"))
